Last glacial cycle glacier erosion potential in the Alps \large \newline Supplementary figures

### 2021-06-11 articles/erosion/alps-erosion-supplement.tex
Add climate sensitivity plots in supplement.

    This document contains copies of the main text Figs. 1--5, and their
    equivalent using the other tested erosion laws.

@@

@@

%\clearpage
\bibliographystyle{copernicus}
\bibliography{../../../references/references}

>>>>

    This document contains copies of the main text Figs. 1--5, and their
    equivalent using the other tested erosion laws. Note that colour levels and
    vertical axes were adapted to the magnitude of the results. Potential
    erosion rates aggregated in time, space and elevation bands, and used to
    plot these figures were made available in a long-term online archive
    \citep[\doi{10.5281/zenodo.4495419}]{Seguinot.2021}.

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_sensitivity}}
      \caption[
        Climate sensitivity of cumulative erosion potential after
        \citet{Koppes.etal.2015}, same as main text Fig. 5.
      ]{%
        Modelled cumulative glacial erosion potential over the last glacial
        cycle using three different paleo-temperature histories from
        \textbf{(a, d)} the Greenland Ice Core Project
        \citep[GRIP;][]{Dansgaard.etal.1993}, \textbf{(b, e)} the European
        Project for Ice Coring in Antarctica \citep[our default,
        EPICA;][]{Jouzel.etal.2007}, and \textbf{(c, f)} an oceanic sediment
        core from the Iberian margin \citep[MD01-2444;][]{Martrat.etal.2007},
        and both \textbf{(a--c)} without and \textbf{(d--f)} with
        paleo-precipitation reductions \citep[cf.][]{Seguinot.etal.2018}.
        After \citet{Koppes.etal.2015}, same as main text Fig. 5.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_sensitivity_her2015}
      \caption{%
        Climate sensitivity of cumulative erosion potential after
        \citet{Herman.etal.2015}.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_sensitivity_hum1994}
      \caption{%
        Climate sensitivity of cumulative erosion potential after
        \citet{Humphrey.Raymond.1994}}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_sensitivity_coo2020}
      \caption{%
        Climate sensitivity of cumulative erosion potential after
        \citet{Cook.etal.2020}}
    \end{figure*}

@@

\clearpage
\bibliographystyle{copernicus}
\bibliography{../../../references/references}
